The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2012-12-20 script/en/chapters/primes.tex
CT script: Minor formal changes in chapter 4

  \item Benford's law\label{primes:Benford-Law}\footnote{%
        \url{http://en.wikipedia.org/wiki/Benford%27s_law}, \\
        \url{http://arxiv.org/PS_cache/arxiv/pdf/0906/0906.2789v1.pdf}. 
        }$^,$\footnote{%
        Two good didactical articles in German about applications of
        Benford's law are:
      \begin{itemize}	
       \item R\"udeger Baumann: "Ziffernanalyse zwecks Betrugsaufdeckung ---
            Beispiel f\"ur kompetenzorientierten und kontextbezogenen
            Informatikunterricht",\\
            in LOGIN, Informatische Bildung und Computer in der Schule,
            No. 154/155, 2008, p. 68-72
       \item Norbert Hungerb\"uhler: "Benfords Gesetz \"uber f\"uhrende
             Ziffern",\\
             March 2007,
             \url{http://www.educ.ethz.ch/unt/um/mathe/ana/benford}
      \end{itemize}

        }
    does not apply to primes.

@@

    Which empirical data applies to this "law" ist not completely clear yet.
    Timo Eckhardt analyzed in his thesis in 2008 extensively attributes of
    prime numbers. Among other things all primes until 7,052,046,499 were
    described with different bases of the positional notation.

@@

   At the end of chapter \ref{nt:NoteFactorization},
   section \hyperlink{RSA-200-chap3}{RSA-200}
   you can see the dimensions of the numbers where the current algorithms
   testing for primality\index{Primality testing} and
   calculating the factorization\index{Factorization!factoring records}
   deliver results.

>>>>

  \item Benford's law\label{primes:Benford-Law}\footnote{%
        \url{http://en.wikipedia.org/wiki/Benford%27s_law}, \\
        \url{http://arxiv.org/PS_cache/arxiv/pdf/0906/0906.2789v1.pdf}. 
        }$^,$\footnote{%
        Two good didactical articles in German about applications of
        Benford's law are:
      % \begin{itemize}	
      % \begin{itemize}[topsep=0pt, itemsep=0pt] 
      % \begin{itemize} \itemsep0pt \parskip0pt \parsep0pt
      % \begin{itemize}              [noitemsep,topsep=0pt,parsep=0pt,parskip=0pt,partopsep=0pt]
        \begin{compactitem}
       \item R\"udeger Baumann: "Ziffernanalyse zwecks Betrugsaufdeckung ---
            Beispiel f\"ur kompetenzorientierten und kontextbezogenen
            Informatikunterricht",\\
            in LOGIN, Informatische Bildung und Computer in der Schule,
            No. 154/155, 2008, p. 68-72
       \item Norbert Hungerb\"uhler: "Benfords Gesetz \"uber f\"uhrende
             Ziffern",\\
             March 2007,
             \url{http://www.educ.ethz.ch/unt/um/mathe/ana/benford}
      %\end{itemize}
      \end{compactitem}
      \vspace{-\baselineskip} % TODO: Geht das nicht anders?
        }
    does not apply to primes.

@@

    Which empirical data applies to this "law" ist not completely clear yet.
    Timo Eckhardt analyzed in his thesis in 2008 extensively attributes of
    prime numbers. %Among other things
    For example, all primes until 7,052,046,499 were
    described with different bases of the positional notation.

@@

   At the end of chapter \ref{nt:NoteFactorization},
   section \hyperlink{RSA-200-chap3}{RSA-200} you can see the limits for which
   numbers the current algorithms for primality testing\index{Primality testing}
   and for factorization\index{Factorization!factoring records}
   deliver good results.
